---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ClassTools

<!-- badges: start -->
<!-- badges: end -->

The ClassTools package has a set of functions that are useful for downloading
material related to classes from GitHub. This package should forked to create a
package that is designed for a particular class. All material for a specific class
should be put in the ClassMaterial directory. Additional R code useful for
specific classes can be added to the R/ directory. 


## Installation

This package should not be installed. Instead it should
be forked from [GitHub](https://github.com/emeyers/ClassTools).  

Here are directions on how to make the necessary changes to turn the ClassTools
package into a class specific package:

1) Fork ClassTools repository to a new GitHub repo. Here are directions on how
to fork my own package: https://deanmalone.net/post/how-to-fork-your-own-repo-on-github/

2) In the DESCRIPTION file rename the package

3) Rename the ClassTools.RProj file

4) In get_package_and_url_names.R change the package_name variable

5) In testthat/testthat.R change library(ClassTools) and test_check("ClassTools")

6) Push changes to GitHub and run devtools::test()

7) Edit the Readme.Rmd to list information relevant to the class


## Example of forked package in use

Here is an example of a forked package used in a class:
https://github.com/emeyers/SDS230


## How to use the package


### Getting homework

How homework should be R Markdown files put in the ClassMaterial/homework
directory. Homework should be named `homework_XX.Rmd`, where `XX` is a two digit
number. For example, the first homework should be called `homework_01.Rmd`. Once
a homework file is created students can download it using the code below.

```{r download_hw, eval = FALSE}
# download the first homework
download_homework(1)
```


### Updating the package

New functions can be added to the package mid-semester by adding new .R files to
the R/ directory. One should also update the version number in the DESCRIPTION
file so that one can check that the updates have taken place. Students can then
update the class package to have access to these function by running the
`reinstall_package()` function.

```{r update_package, eval = FALSE}
# reinstall the package from GitHub to contain updated functions.
reinstall_package()
```


### Updating installed packages

A list of packages that students should have installed is in the file
ClassMaterial/required_package.txt. Package names should be on new lines
separated by commas (similar to how they are listed in the Imports line of the
DESCRIPTION file). Students can then install all the required class packages
using the `update_installed_packages()` function

```{r install_class_packages, eval = FALSE}
# install any packages used in the class
update_installed_packages()
```










